\section*{Selected Publications}


%For invited talks, lectures, and tutorials, refer to \url{https://wilkeraziz.github.io/talks.html}.


%\paragraph{Selected publications} ~ representative of my current interests
\begin{itemize}
	 \setlength\itemsep{1pt}
	\item \emph{Is MAP Decoding All You Need? The Inadequacy of the Mode in Neural Machine Translation}.\\
	Bryan Eikema and Wilker Aziz. In \emph{Coling}, 2020. 
	\item \emph{Efficient Marginalization of Discrete and Structured Latent Variables via Sparsity}.\\
	Gonçalo M. Correia, Vlad Niculae, Wilker Aziz, and André F. T. Martins. In \emph{NeurIPS}, 2020. 
	\item \emph{Effective Estimation of Deep Generative Language Models}.\\
	Tom Pelsmaeker and Wilker Aziz. In \emph{ACL}, 2020. 
	\item \emph{A Latent Morphology Model for Open-Vocabulary Neural Machine Translation}.\\
	Duygu Ataman, Wilker Aziz, and Alexandra Birch. In \emph{ICLR}, 2020. 
	\item \emph{Interpretable Neural Predictions with Differentiable Binary Variables}.\\
	Jasmijn Bastings, Wilker Aziz and Ivan Titov. In \emph{ACL}, 2019. 
	\item \emph{Block Neural Autoregressive Flow}.\\
	Nicola De Cao, Wilker Aziz and Ivan Titov. In \emph{UAI}, 2019. 
	\item \emph{Question Answering by Reasoning Across Documents with Graph Convolutional Networks}.\\
	Nicola De Cao, Wilker Aziz and Ivan Titov. In \emph{NAACL}, 2019.
	\item \emph{A Stochastic Decoder for Neural Machine Translation}.\\
	Philip Schulz, Wilker Aziz and Trevor Cohn. In \emph{ACL}, 2018. 
	\item \emph{Fast collocation-based Bayesian HMM word alignment}. \\
	Philip Schulz and Wilker Aziz. In \emph{COLING}, 2016. 
	\item \emph{Exact Decoding for Phrase-Based Statistical Machine Translation}. \\
	Wilker Aziz, Marc Dymetman and Lucia Specia. In \emph{EMNLP}, 2014.
\end{itemize}

For a complete list refer to \url{https://wilkeraziz.github.io/publications.html}. 

%\paragraph{Complete list}

%\begin{btSect}{bib}
%\btPrintNotCited
%\end{btSect}

